---
title       : "Car Accessability"
subtitle    : 
author      : 
job         : 
framework   : deckjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : swiss      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Car Acceptability 


--- .class #id

## Introduction


> * The data used in the project is retreived from car.data dataset provided in the R "datasets" package.
> * There are 7 variables in the dataset (Car acceptability, Price, Doors, Persons, Space for luggage, Safety, Comfort)
> * The number of observations is 1728


```{r table, results='asis', warning=TRUE, echo=FALSE}
library(knitr)

carTable = read.table("assets/car.data", sep=",")
carDS = as.data.frame(carTable)



kable(head(carDS), format ="markdown", row.names=NA, caption="Except from the car acceptability dataset", col.names=c("|  Car acceptability  |", "|  Price   |", "|  Doors   |", "|  Persons   |", "|  Luggage Boot   |", "|  Safety   |", "|  Comfort   |"))
#pander(head(carTable), style="rmarkdown", split.cells = Inf)

colnames(carDS) = c("car_acceptability", "price", "doors", "persons", "lug_boot", "safety", "comfort")
```

--- .class #id

## App features
> * Easy to modify the model
> * Option to modify the variables which are included in the model
> * Max depth parameter for fine tuning the model
> * Great way to visualize the solution
> * Easy to determine which factors are important for determining the car accessability
> * You can access the application by visiting: https://lennyvis.shinyapps.io/Specialization

--- .class #id

## Example of a visualized model
```{r, cache=TRUE, warning=FALSE, echo=FALSE}

library(shiny)
library(caret)
library(rattle)
library(rpart)
library(e1071)
library(rpart.plot)
library(datasets)

cvCtrl <- trainControl(method = "cv", number=5, allowParallel = TRUE)
gmbGrid = expand.grid(maxdepth=c(2:3))
trainObjRPART = train(car_acceptability~., data=carDS, method="rpart2", trControl = cvCtrl, tuneGrid = gmbGrid)
fancyRpartPlot(trainObjRPART$finalModel, main="Car acceptability", sub="")
```

--- .class #id

## Conclusion

> * Comfort is the most important parameter when determining the car acceptability level
> * Changing the depth level for the tree affects the model
> * The depth of the tree is affected by the number of parameters we choose


--- .class #id
